Haul-out behavior and aerial survey detectability of seals in the Bering and Chukchi seas

### 2022-04-07 analysis/paper/London_HauloutBeahvior.Rmd
confirm inclusion of Nuiqsut; closes #24

Data used in our study came from bio-loggers deployed on bearded, ribbon, and
spotted seals in the Bering, Chukchi, and western Beaufort seas by multiple
organizations as part of collaborative investigations from 2005 through 2020.
Seals were captured using nets and bio-loggers were attached during studies based
in coastal Alaska communities or on research ships. Ship-based capture events
occurred during spring near the southern ice edge in the Bering Sea. Land-based
capture events occurred from May to October, generally between the coastal
communities of Scammon Bay, Alaska in the Bering Sea, Utqiaġvik, Alaska in the
Chukchi Sea, and Nuiqsut in the Beaufort Sea from 2005 to 2020. We refer readers
to the primary literature for detailed capture and bio-logger attachment methods
(see Supplemental Material, Table 1).

>>>>

Data used in our study came from bio-loggers deployed on bearded, ribbon, and
spotted seals in the Bering, Chukchi, and western Beaufort seas by multiple
organizations as part of collaborative investigations from 2005 through 2020.
Seals were captured using nets and bio-loggers were attached during studies
based in coastal Alaska communities or on research ships. Ship-based capture
events occurred during spring near the southern ice edge in the Bering Sea.
Land-based capture events occurred between 2005 and 2020 from May to October,
generally between the coastal communities of Scammon Bay, Alaska in the Bering
Sea, Utqiaġvik, Alaska in the Chukchi Sea, and Nuiqsut in the Beaufort Sea. We
refer readers to the primary literature for detailed capture and bio-logger
attachment methods (see Supplemental Material, S1).
